A Secondary Screen Architecture to Accurately Capture Viewers' Interactions in an iTV Environment

### 2014-06-04 src/paper.tex
Abstract changed

\title{A secondary screen architecture to accurately capture viewers' interactions in an iTV environment}

@@

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watching TV. Since the TV set is shared by many people and the interaction occurs by using a single remote control, it is difficult to accurately capture the individual needs from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage uniquely who is present in the environment and what is being watched on TV. In this paper, it is presented a novel architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application for this data consists of generating personalized content for single viewers and groups of viewers.
\end{abstract}

>>>>

\title{A Secondary Screen Architecture to Accurately Capture Viewers' Interactions in an iTV Environment}

@@

\begin{abstract}
Advances in TV technology have enabled viewers to actively interact with the TV through interactive applications instead of just passively watching TV. Typically, a conventional remote control is shared by many viewers and it is difficult to accurately capture the individual interaction data from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage precisely who is present in the environment and what is being watched on TV. In this paper, it is presented a novel architecture that facilitates the capture of viewers' individual interactions and contextual data in shared TV environments. This architecture uses personal devices as secondary screen devices with the aim of identifying viewers and capturing their interactions with interactive TV devices. One important application for this data consists of generating personalized content for single viewers and groups of viewers.
\end{abstract}
